### 2022-11-19 dissertation/chapters/08-results.tex
🚧 (results): BHH vs Low Level Heuristics

This section provides the empirical results for the experimental group that compares the performance of the \acs{BHH} to the performance of the individual, standalone, low-level heuristics. Detailed discussions and illustrations follow. As a reminder, the set of low-level heuristics include a number of gradient-based heuristics and a number of meta-heuristics. Three different variants of the \acs{BHH} is included in the experiment, including the \acs{BHH} baseline configuration with a \index{heuristic pool}heuristic pool that contains all the low-level heuristics (denoted bhh\_all), the \acs{BHH} configuration with a \index{heuristic pool}heuristic pool that contains only gradient-based \index{heuristic}heuristics (denoted bhh\_gd), and finally, a \acs{BHH} configuration with a \index{heuristic pool}heuristics pool that contains only \index{meta-heuristic}meta-heuristics (denoted bhh\_mh).

Table~\ref{tab:results:standalone:metrics:test_loss} presents the empirical results for this experimental group, showing the average test loss and statistics for all the low-level heuristics, compared to the three variants of the \acs{BHH} that was implemented. The test loss that is reported in Table~\ref{tab:results:standalone:metrics:test_loss} reflects on the test loss achieved at the last epoch of training, across all datasets, averaged over all independent runs.

@@

	\caption{Empirical results showing normalised average rank and statistics for different low-level \index{heuristic}heuristics compared to 3 \index{heuristic pool}heuristic pool variants of the baseline \acs{BHH} across multiple datasets, for all runs and epochs.}

@@

			                             & \multicolumn{13}{c}{\textbf{BHH vs. Low-Level Heuristics - Average Rank}}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              \\

@@

	\caption{Empirical results showing normalised average rank and statistics for different low-level \index{heuristic}heuristics compared to 3 \index{heuristic pool}heuristic pool variants of the baseline \acs{BHH} across multiple datasets, for all runs and epochs.}
			                                    & \multicolumn{13}{c}{\textbf{BHH vs. Low-Level Heuristics - Average Loss}}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                         \\

From Table~\ref{tab:results:standalone:metrics:test_loss} it can be seen that the bhh\_gd configuration produced the best results of the \acs{BHH} variants and managed to perform well, producing generally good results across all datasets. The bhh\_gd configuration managed to produced results comparable to the best heuristics for each dataset, while the bhh\_all and bhh\_mh produced average results compared to all the \index{heuristic}heuristics. One exception stands out, and that is for the for bhh\_all configuration. The bhh\_all configuration produced bad results for the adult dataset, yielding an average loss far greater than any of the other implementations. More detailed discussions on this specific case is provided later in the Chapter.

Table~\ref{tab:results:standalone:metrics:rank} provides the empirical results in ranking format. The performance rank is calculated as the average rank produced by each \index{heuristic}heuristic, for all datasets, over all runs and all training epochs. The average rank across all epochs produce a view on the performance of the \index{heuristic}heuristics as it relates to the entire training process. Finally, a normalised average rank is provided for the overall performance of all \index{heuristic}heuristics at the bottom of the table. From the normalised average ranks, it can be seen that the bhh\_gd configuration ranked fourth, while the bhh\_all and bhh\_mh configurations ranked sixth and 8th amongst all thirteen \index{heuristic}heuristic implementations respectively.
	\caption{Empirical results showing average test loss and statistics for different low-level \index{heuristic}heuristics compared to 3 \index{heuristic pool}heuristic pool variants of the baseline \acs{BHH} across multiple datasets, for all runs, at the last epoch.}
	\label{tab:results:standalone:metrics:test_loss}%
		% Table generated by Excel2LaTeX from sheet 'loss'
			                                    & \multicolumn{13}{c}{\textbf{BHH vs. Low-Level Heuristics - Average Loss}}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                         \\

Figure~\ref{fig:results:standalone:descriptive:descriptive} provides an illustration showing a descriptive plot of the average ranks across all runs for each \index{heuristic}heuristic, per dataset.

\begin{figure}[htb]
	\centering
	\includegraphics[width=\textwidth]{standalone/figures/descriptive/descriptive.pdf}
	\caption{Descriptive plots for the average ranks of all low-level heuristics compared to 3 \index{heuristic pool}heuristic pool variants of the baseline \Acs{BHH} per dataset, across all runs and epochs.}
	\label{fig:results:standalone:descriptive:descriptive}
\end{figure}

@@

Although the outcomes of the bhh\_all and bhh\_mh configurations seem to produce average performance results, it should be noted that the performance difference between all \index{heuristic}heuristics is very small. Furthermore, the best configuration of the \acs{BHH}, namely the bhh\_gd configuration, was statistically only outperformed overall by \acs{Adagrad}, yielding statistically comparable results than \acs{Adam}, \acs{NAG} and \acs{RMSProp}. It should be noted that the standalone low-level \index{heuristic} \index{heuristic}heuristics already produce good results in general across all datasets. In this particular case, producing better performance outcomes can be hard to achieve. However, the \acs{BHH} provides a generalisation capability across all datasets that is advantageous to the \acs{BHH}.

Another observation that can be made is that the gradient-based \index{heuristic}heuristics generally performed much better than the \index{meta-heuristic}meta-heuristics on all datasets. State of the art methods for training \acp{FFNN} such as \acs{Adam}, utilise gradient-based approaches that have been proven to work well on many occasions~\cite{ref:kingma:2014}. Exploration of the \index{heuristic}heuristic space leads the \acs{BHH} to consider other \index{heuristic}heuristics during the training process, which could possibly result in worse performances at times. As previously mentioned, a suggestion to improve on these results is to include a move-acceptance strategy, where heuristic progressions are discarded if they fail to produce better results.

Figures~\ref{fig:results:standalone:figures:iris}-\ref{fig:results:standalone:figures:car} provide illustrations of the train and test, loss and accuracy plots for each heuristics as it relates to a selection of classification datasets. The train and test, loss and accuracy plots provided are illustrated in log scale. The other classification datasets are left out for brevity as they produce similar illustrations.

\begin{figure}[htb]
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{standalone/figures/train/loss/iris.pdf}
		\caption{Train log loss}
		\label{fig:results:standalone:figures:loss:train:iris}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{standalone/figures/test/loss/iris.pdf}
		\caption{Test log loss}
		\label{fig:results:standalone:figures:loss:test:iris}
	\end{subfigure}
	\par\bigskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{standalone/figures/train/accuracy/iris.pdf}
		\caption{Train log accuracy}
		\label{fig:results:standalone:figures:accuracy:train:iris}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{standalone/figures/test/accuracy/iris.pdf}
		\caption{Test log accuracy}
		\label{fig:results:standalone:figures:accuracy:test:iris}
	\end{subfigure}
	\par\bigskip
	\caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level \index{heuristic}heuristics on the iris dataset over 30 epochs, illustrated in log scale.}
	\label{fig:results:standalone:figures:iris}
\end{figure}

\begin{figure}[htb]
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{standalone/figures/train/loss/bank.pdf}
		\caption{Train log loss}
		\label{fig:results:standalone:figures:loss:train:bank}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{standalone/figures/test/loss/bank.pdf}
		\caption{Test log loss}
		\label{fig:results:standalone:figures:loss:test:bank}
	\end{subfigure}
	\par\bigskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{standalone/figures/train/accuracy/bank.pdf}
		\caption{Train log accuracy}
		\label{fig:results:standalone:figures:accuracy:train:bank}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{standalone/figures/test/accuracy/bank.pdf}
		\caption{Test log accuracy}
		\label{fig:results:standalone:figures:accuracy:test:bank}
	\end{subfigure}
	\par\bigskip
	\caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level \index{heuristic}heuristics on the bank dataset over 30 epochs, illustrated in log scale.}
	\label{fig:results:standalone:figures:bank}
\end{figure}

\begin{figure}[htb]
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{standalone/figures/train/loss/car.pdf}
		\caption{Train log loss}
		\label{fig:results:standalone:figures:loss:train:car}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{standalone/figures/test/loss/car.pdf}
		\caption{Test log loss}
		\label{fig:results:standalone:figures:loss:test:car}
	\end{subfigure}
	\par\bigskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{standalone/figures/train/accuracy/car.pdf}
		\caption{Train log accuracy}
		\label{fig:results:standalone:figures:accuracy:train:car}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{standalone/figures/test/accuracy/car.pdf}
		\caption{Test log accuracy}
		\label{fig:results:standalone:figures:accuracy:test:car}
	\end{subfigure}
	\par\bigskip
	\caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level \index{heuristic}heuristics on the car dataset over 30 epochs, illustrated in log scale.}
	\label{fig:results:standalone:figures:car}
\end{figure}

Figures~\ref{fig:results:standalone:figures:fish_toxicity}-\ref{fig:results:standalone:figures:parkinsons} provide illustrations of the train and test loss plots for each heuristics as it relates to a selection of regression datasets. The train and test loss plots provided are illustrated in log scale. Similar to before, the other regression datasets are left out for brevity as they produce similar illustrations.

\begin{figure}[htb]
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{standalone/figures/train/loss/fish_toxicity.pdf}
		\caption{Train log loss}
		\label{fig:results:standalone:figures:loss:train:fish_toxicity}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{standalone/figures/test/loss/fish_toxicity.pdf}
		\caption{Test log loss}
		\label{fig:results:standalone:figures:loss:test:fish_toxicity}
	\end{subfigure}
	\par\bigskip
	\caption{The train and test loss plots for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level \index{heuristic}heuristics on the fish toxicity dataset over 30 epochs, illustrated in log scale.}
	\label{fig:results:standalone:figures:fish_toxicity}
\end{figure}

\begin{figure}[htb]
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{standalone/figures/train/loss/parkinsons.pdf}
		\caption{Train log loss}
		\label{fig:results:standalone:figures:loss:train:parkinsons}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{standalone/figures/test/loss/parkinsons.pdf}
		\caption{Test log loss}
		\label{fig:results:standalone:figures:loss:test:parkinsons}
	\end{subfigure}
	\par\bigskip
	\caption{The train and test loss plots for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level \index{heuristic}heuristics on the parkinsons dataset over 30 epochs, illustrated in log scale.}
	\label{fig:results:standalone:figures:parkinsons}
\end{figure}

@@

	\caption{Empirical results showing average rank and statistics for all heuristic pool configurations used by the \acs{BHH} across multiple datasets, for all runs and epochs.}

@@

	\caption{Empirical results showing average rank and statistics for different population sizes used by the \acs{BHH} across multiple datasets, for all runs and all epochs.}

@@

	\caption{Empirical results showing average rank and statistics for different credit assignment strategies used by the \acs{BHH} across multiple datasets, for all runs and epochs.}

@@

	\caption{Empirical results showing average rank and statistics for different reselection intervals used by the \acs{BHH} across multiple datasets, for all runs and epochs.}

@@

	\caption{Empirical results showing average rank and statistics for different replay window sizes used by the \acs{BHH} across multiple datasets, for all runs and epochs.}

@@

	\caption{Empirical results showing average rank and statistics for different reanalysis intervals used by the \acs{BHH} across multiple datasets, for all runs and epochs.}

@@

	\caption{Empirical results showing average rank and statistics for different burn in window sizes used by the \acs{BHH} across multiple datasets, for all runs and epochs.}

@@

\begin{table}[htb]
	\centering
	\caption{Empirical results showing average rank and statistics for normalisation toggled by the \acs{BHH} across multiple datasets, for all runs and epochs.}
	\label{tab:results:normalise:metrics:loss}%
	\par\bigskip
	\resizebox{0.6\textwidth}{!}{
		\begin{tabular}{r|cc}
			                             & \multicolumn{2}{c}{\textbf{Normalisation - Average Loss}}                                                           \\
			\midrule
			\textbf{dataset}             & \textbf{false}                                            & \textbf{true}                                           \\
			\midrule
			\textbf{abalone}             & \cellcolor[rgb]{ .388,  .745,  .482}2.0587 ($\pm$0.088)   & \cellcolor[rgb]{ .973,  .412,  .42}2.0936 ($\pm$0.231)  \\
			\textbf{air quality}         & \cellcolor[rgb]{ .973,  .412,  .42}0.2729 ($\pm$0.016)    & \cellcolor[rgb]{ .388,  .745,  .482}0.2704 ($\pm$0.017) \\
			\textbf{bank}                & \cellcolor[rgb]{ .973,  .412,  .42}0.2456 ($\pm$0.065)    & \cellcolor[rgb]{ .388,  .745,  .482}0.2374 ($\pm$0.042) \\
			\textbf{bike}                & \cellcolor[rgb]{ .388,  .745,  .482}0.0651 ($\pm$0.02)    & \cellcolor[rgb]{ .973,  .412,  .42}0.0689 ($\pm$0.03)   \\
			\textbf{car}                 & \cellcolor[rgb]{ .388,  .745,  .482}0.1572 ($\pm$0.034)   & \cellcolor[rgb]{ .973,  .412,  .42}0.1721 ($\pm$0.038)  \\
			\textbf{diabetic}            & \cellcolor[rgb]{ .388,  .745,  .482}1.2983 ($\pm$0.66)    & \cellcolor[rgb]{ .973,  .412,  .42}1.5051 ($\pm$1.93)   \\
			\textbf{fish toxicity}       & \cellcolor[rgb]{ .973,  .412,  .42}0.1046 ($\pm$0.008)    & \cellcolor[rgb]{ .388,  .745,  .482}0.1021 ($\pm$0.009) \\
			\textbf{forest fires}        & \cellcolor[rgb]{ .388,  .745,  .482}0.081 ($\pm$0.069)    & \cellcolor[rgb]{ .973,  .412,  .42}0.0868 ($\pm$0.069)  \\
			\textbf{housing}             & \cellcolor[rgb]{ .973,  .412,  .42}0.0941 ($\pm$0.017)    & \cellcolor[rgb]{ .388,  .745,  .482}0.0931 ($\pm$0.019) \\
			\textbf{iris}                & \cellcolor[rgb]{ .973,  .412,  .42}0.2411 ($\pm$0.295)    & \cellcolor[rgb]{ .388,  .745,  .482}0.2358 ($\pm$0.333) \\
			\textbf{mushroom}            & \cellcolor[rgb]{ .388,  .745,  .482}0.0052 ($\pm$0.012)   & \cellcolor[rgb]{ .973,  .412,  .42}0.0455 ($\pm$0.216)  \\
			\textbf{parkinsons}          & \cellcolor[rgb]{ .388,  .745,  .482}0.0587 ($\pm$0.003)   & \cellcolor[rgb]{ .973,  .412,  .42}0.0598 ($\pm$0.004)  \\
			\textbf{student performance} & \cellcolor[rgb]{ .388,  .745,  .482}0.2359 ($\pm$0.102)   & \cellcolor[rgb]{ .973,  .412,  .42}0.2522 ($\pm$0.098)  \\
			\textbf{wine quality}        & \cellcolor[rgb]{ .388,  .745,  .482}1.0827 ($\pm$0.026)   & \cellcolor[rgb]{ .973,  .412,  .42}1.0831 ($\pm$0.045)  \\
		\end{tabular}%
	}
\end{table}%

>>>>

This section provides the empirical results for the experimental group that compares the performance of the \acs{BHH} to the performance of the individual, standalone, low-level heuristics. Detailed discussions and illustrations follow. As a reminder, the set of low-level heuristics includes a number of gradient-based heuristics and a number of meta-heuristics. Three variants of the \acs{BHH} is included in the experiment, including the \acs{BHH} baseline configuration with a \index{heuristic pool}heuristic pool that contains all the low-level heuristics (denoted bhh\_all), the \acs{BHH} configuration with a \index{heuristic pool}heuristic pool that contains only gradient-based \index{heuristic}heuristics (denoted bhh\_gd), and finally, the \acs{BHH} configuration with a \index{heuristic pool}heuristics pool that contains only \index{meta-heuristic}meta-heuristics (denoted bhh\_mh).

Table~\ref{tab:results:standalone:metrics:loss} presents the empirical results for this experimental group, showing the average test loss and statistics for all the low-level heuristics, compared to the three variants of the \acs{BHH} that was implemented. The test loss is measured at the last epoch for each dataset, over all indepedent runs.

@@

	\caption{Empirical results showing test loss and statistics for different low-level \index{heuristic}heuristics compared to three \index{heuristic pool}heuristic pool variants of the \acs{BHH} baseline configuration, across multiple datasets, for all independent runs, measured at the last epoch.}
			                                    & \multicolumn{13}{c}{\textbf{BHH vs. Low-Level Heuristics - Average Test Loss}}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                         \\
\end{sidewaystable}%

From Table~\ref{tab:results:standalone:metrics:loss} it can be seen that the bhh\_gd configuration produced the best results of the \acs{BHH} variants and managed to perform well, producing generally good results across all datasets. The bhh\_gd configuration managed to produce results that are comparable to the top three heuristics for each dataset, while the bhh\_all and bhh\_mh produced average results compared to all the \index{heuristic}heuristics.

Table~\ref{tab:results:standalone:metrics:rank} provides the empirical results from Table~\ref{tab:results:standalone:metrics:loss} in ranked format. The performance rank is calculated as the average rank produced by each \index{heuristic}heuristic, across all datasets, for all indepented runs and all epochs. The average rank across all epochs produces a view on the performance of the \index{heuristic}heuristics as it relates to the entire training process. Finally, a normalised average rank is provided for the overall performance of all \index{heuristic}heuristics at the bottom of the table. The normalised average rank is calculated as a discrete normalisation of the average rank achieved across all datasets, for all independent runs and epochs.
	\caption{Empirical results showing normalised average rank and statistics for different low-level \index{heuristic}heuristics compared to three \index{heuristic pool}heuristic pool variants of the \acs{BHH} baseline configuration, across multiple datasets, for all independent runs and epochs.}

@@

			                             & \multicolumn{13}{c}{\textbf{BHH vs. Low-Level Heuristics - Average Rank (Based on Test Loss)}}                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                              \\

@@

From the normalised average ranks provided in Table~\ref{tab:results:standalone:metrics:rank}, it can be seen that the bhh\_gd configuration ranked fourth, while the bhh\_all and bhh\_mh configurations ranked sixth and eigth amongst all thirteen \index{heuristic}heuristic implementations respectively. These results show that the \acs{BHH} generally performs well, but is not able to outperform the best heuristic for each dataset.

Figure~\ref{fig:results:standalone:descriptive:descriptive} provides an illustration showing a descriptive plot of the average ranks achieved over all independent runs, for each \index{heuristic}heuristic, per dataset. The heuristics are ordered according to the normalised ranks presented in Table~\ref{tab:results:standalone:metrics:rank}.

\begin{figure}[htb]
	\centering
	\includegraphics[width=\textwidth]{standalone/figures/descriptive/descriptive.pdf}
	\caption{Descriptive plots for the average ranks of all low-level heuristics compared to three \index{heuristic pool}heuristic pool variants of the \acs{BHH} baseline configuration, per dataset, across all runs and epochs.}
	\label{fig:results:standalone:descriptive:descriptive}
\end{figure}

From Figure~\ref{fig:results:standalone:descriptive:descriptive} a few observations can be made. Firstly, both \acs{Adam} and \acs{RMSProp} achieved radically different average ranks for the student performance dataset, compared to the other datasets. This can also be see in Table~\ref{tab:results:standalone:metrics:rank}. Further investigation into the reasons for this is required as both these heuristics perform well on all other datasets, and the other heuristics perform well for the student performance dataset. A suggestions then leads to the possibility that an invalid learning rate or learning rate schedule leads to a scenario where good solutions are overshot, causing \acs{Adam} and \acs{RMSProp} to struggle to resolve back to good solutions. Furthermore, the bhh\_gd heuristic achieved the lowest variance in average rank across all datasets, compared to the other heuristics. The aforementioned shows the generalisation capabilities of the \acs{BHH} to multiple problems.

@@

Although the outcomes of the bhh\_all and bhh\_mh configurations seem to produce average performance results, it should be noted that the performance difference between all \index{heuristic}heuristics is very small. Furthermore, the best configuration of the \acs{BHH}, namely the bhh\_gd configuration, was statistically only outperformed overall by \acs{Adagrad} and \acs{Adam}, yielding statistically comparable results to \acs{RMSProp} and \acs{NAG}. It should be noted that the standalone low-level \index{heuristic} \index{heuristic}heuristics already produce good results in general across all datasets. In this particular case, producing better performance outcomes can be hard to achieve. However, as mentioned previously, the \acs{BHH} provides a generalisation capability across all datasets that is advantageous to the \acs{BHH}.

Another observation that can be made is that the gradient-based \index{heuristic}heuristics generally performed much better than the \index{meta-heuristic}meta-heuristics on all datasets. State of the art methods for training \acp{FFNN}, such as \acs{Adam}, utilise gradient-based approaches that have been proven to work well on many occasions~\cite{ref:kingma:2014}. Exploration of the \index{heuristic}heuristic space leads the \acs{BHH} to consider other \index{heuristic}heuristics during the training process, which could possibly result in worse performances at times. As previously mentioned, a suggestion to improve on these results is to include a move-acceptance strategy, where heuristic progressions are discarded if they fail to produce better results.

Figures~\ref{fig:results:standalone:figures:iris}-\ref{fig:results:standalone:figures:bank} provide example illustrations of the train and test, loss and accuracy plots for each heuristic as it relates to a selection of classification datasets. The train and test, loss and accuracy plots provided are illustrated in log scale. The other classification datasets are left out for brevity as they produce similar illustrations.

\begin{figure}[htpb]
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{standalone/figures/train/loss/iris.pdf}
		\caption{Train log loss}
		\label{fig:results:standalone:figures:loss:train:iris}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{standalone/figures/test/loss/iris.pdf}
		\caption{Test log loss}
		\label{fig:results:standalone:figures:loss:test:iris}
	\end{subfigure}
	\par\bigskip
	\par\bigskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{standalone/figures/train/accuracy/iris.pdf}
		\caption{Train log accuracy}
		\label{fig:results:standalone:figures:accuracy:train:iris}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{standalone/figures/test/accuracy/iris.pdf}
		\caption{Test log accuracy}
		\label{fig:results:standalone:figures:accuracy:test:iris}
	\end{subfigure}
	\par\bigskip
	\caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level \index{heuristic}heuristics on the iris dataset over 30 epochs, illustrated in log scale.}
	\label{fig:results:standalone:figures:iris}
\end{figure}

\begin{figure}[htpb]
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{standalone/figures/train/loss/car.pdf}
		\caption{Train log loss}
		\label{fig:results:standalone:figures:loss:train:car}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{standalone/figures/test/loss/car.pdf}
		\caption{Test log loss}
		\label{fig:results:standalone:figures:loss:test:car}
	\end{subfigure}
	\par\bigskip
	\par\bigskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{standalone/figures/train/accuracy/car.pdf}
		\caption{Train log accuracy}
		\label{fig:results:standalone:figures:accuracy:train:car}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{standalone/figures/test/accuracy/car.pdf}
		\caption{Test log accuracy}
		\label{fig:results:standalone:figures:accuracy:test:car}
	\end{subfigure}
	\par\bigskip
	\caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level \index{heuristic}heuristics on the car dataset over 30 epochs, illustrated in log scale.}
	\label{fig:results:standalone:figures:car}
\end{figure}

\begin{figure}[htpb]
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{standalone/figures/train/loss/bank.pdf}
		\caption{Train log loss}
		\label{fig:results:standalone:figures:loss:train:bank}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{standalone/figures/test/loss/bank.pdf}
		\caption{Test log loss}
		\label{fig:results:standalone:figures:loss:test:bank}
	\end{subfigure}
	\par\bigskip
	\par\bigskip
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{standalone/figures/train/accuracy/bank.pdf}
		\caption{Train log accuracy}
		\label{fig:results:standalone:figures:accuracy:train:bank}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{standalone/figures/test/accuracy/bank.pdf}
		\caption{Test log accuracy}
		\label{fig:results:standalone:figures:accuracy:test:bank}
	\end{subfigure}
	\par\bigskip
	\caption{The train and test loss and accuracy plots for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level \index{heuristic}heuristics on the bank dataset over 30 epochs, illustrated in log scale.}
	\label{fig:results:standalone:figures:bank}
\end{figure}

Figures~\ref{fig:results:standalone:figures:fish_toxicity}-\ref{fig:results:standalone:figures:parkinsons} provide example illustrations of the train and test loss plots for each heuristic as it relates to a selection of regression datasets. The train and test loss plots provided are illustrated in log scale. Similar to before, the other regression datasets are left out for brevity as they produce similar illustrations.

\begin{figure}[htpb]
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{standalone/figures/train/loss/fish_toxicity.pdf}
		\caption{Train log loss}
		\label{fig:results:standalone:figures:loss:train:fish_toxicity}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{standalone/figures/test/loss/fish_toxicity.pdf}
		\caption{Test log loss}
		\label{fig:results:standalone:figures:loss:test:fish_toxicity}
	\end{subfigure}
	\par\bigskip
	\caption{The train and test loss plots for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level \index{heuristic}heuristics on the fish toxicity dataset over 30 epochs, illustrated in log scale.}
	\label{fig:results:standalone:figures:fish_toxicity}
\end{figure}

\begin{figure}[htpb]
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{standalone/figures/train/loss/parkinsons.pdf}
		\caption{Train log loss}
		\label{fig:results:standalone:figures:loss:train:parkinsons}
	\end{subfigure}
	\begin{subfigure}{0.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{standalone/figures/test/loss/parkinsons.pdf}
		\caption{Test log loss}
		\label{fig:results:standalone:figures:loss:test:parkinsons}
	\end{subfigure}
	\par\bigskip
	\caption{The train and test loss plots for the experimental group comparing the performance of the \acs{BHH} to individual, standalone, low-level \index{heuristic}heuristics on the parkinsons dataset over 30 epochs, illustrated in log scale.}
	\label{fig:results:standalone:figures:parkinsons}
\end{figure}

@@

	\caption{Empirical results showing average rank and statistics for all heuristic pool configurations used by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}

@@

	\caption{Empirical results showing average rank and statistics for different population sizes used by the \acs{BHH} across multiple datasets, for all independent runs and all epochs.}

@@

	\caption{Empirical results showing average rank and statistics for different credit assignment strategies used by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}

@@

	\caption{Empirical results showing average rank and statistics for different reselection intervals used by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}

@@

	\caption{Empirical results showing average rank and statistics for different replay window sizes used by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}

@@

	\caption{Empirical results showing average rank and statistics for different reanalysis intervals used by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}

@@

	\caption{Empirical results showing average rank and statistics for different burn in window sizes used by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}

@@

\begin{table}[htb]
	\centering
	\caption{Empirical results showing average rank and statistics for normalisation toggled by the \acs{BHH} across multiple datasets, for all independent runs and epochs.}
	\label{tab:results:normalise:metrics:loss}%
	\par\bigskip
	\resizebox{0.6\textwidth}{!}{
		\begin{tabular}{r|cc}
			                             & \multicolumn{2}{c}{\textbf{Normalisation - Average Loss}}                                                           \\
			\midrule
			\textbf{dataset}             & \textbf{false}                                            & \textbf{true}                                           \\
			\midrule
			\textbf{abalone}             & \cellcolor[rgb]{ .388,  .745,  .482}2.0587 ($\pm$0.088)   & \cellcolor[rgb]{ .973,  .412,  .42}2.0936 ($\pm$0.231)  \\
			\textbf{air quality}         & \cellcolor[rgb]{ .973,  .412,  .42}0.2729 ($\pm$0.016)    & \cellcolor[rgb]{ .388,  .745,  .482}0.2704 ($\pm$0.017) \\
			\textbf{bank}                & \cellcolor[rgb]{ .973,  .412,  .42}0.2456 ($\pm$0.065)    & \cellcolor[rgb]{ .388,  .745,  .482}0.2374 ($\pm$0.042) \\
			\textbf{bike}                & \cellcolor[rgb]{ .388,  .745,  .482}0.0651 ($\pm$0.02)    & \cellcolor[rgb]{ .973,  .412,  .42}0.0689 ($\pm$0.03)   \\
			\textbf{car}                 & \cellcolor[rgb]{ .388,  .745,  .482}0.1572 ($\pm$0.034)   & \cellcolor[rgb]{ .973,  .412,  .42}0.1721 ($\pm$0.038)  \\
			\textbf{diabetic}            & \cellcolor[rgb]{ .388,  .745,  .482}1.2983 ($\pm$0.66)    & \cellcolor[rgb]{ .973,  .412,  .42}1.5051 ($\pm$1.93)   \\
			\textbf{fish toxicity}       & \cellcolor[rgb]{ .973,  .412,  .42}0.1046 ($\pm$0.008)    & \cellcolor[rgb]{ .388,  .745,  .482}0.1021 ($\pm$0.009) \\
			\textbf{forest fires}        & \cellcolor[rgb]{ .388,  .745,  .482}0.081 ($\pm$0.069)    & \cellcolor[rgb]{ .973,  .412,  .42}0.0868 ($\pm$0.069)  \\
			\textbf{housing}             & \cellcolor[rgb]{ .973,  .412,  .42}0.0941 ($\pm$0.017)    & \cellcolor[rgb]{ .388,  .745,  .482}0.0931 ($\pm$0.019) \\
			\textbf{iris}                & \cellcolor[rgb]{ .973,  .412,  .42}0.2411 ($\pm$0.295)    & \cellcolor[rgb]{ .388,  .745,  .482}0.2358 ($\pm$0.333) \\
			\textbf{mushroom}            & \cellcolor[rgb]{ .388,  .745,  .482}0.0052 ($\pm$0.012)   & \cellcolor[rgb]{ .973,  .412,  .42}0.0455 ($\pm$0.216)  \\
			\textbf{parkinsons}          & \cellcolor[rgb]{ .388,  .745,  .482}0.0587 ($\pm$0.003)   & \cellcolor[rgb]{ .973,  .412,  .42}0.0598 ($\pm$0.004)  \\
			\textbf{student performance} & \cellcolor[rgb]{ .388,  .745,  .482}0.2359 ($\pm$0.102)   & \cellcolor[rgb]{ .973,  .412,  .42}0.2522 ($\pm$0.098)  \\
			\textbf{wine quality}        & \cellcolor[rgb]{ .388,  .745,  .482}1.0827 ($\pm$0.026)   & \cellcolor[rgb]{ .973,  .412,  .42}1.0831 ($\pm$0.045)  \\
		\end{tabular}%
	}
\end{table}%
